---
title: "processing"
author: "AGREEMENT"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Read the dataset
```{r}
library(readxl)
datos <- read_xlsx("pone.0168321.s003.xlsx")
datos
```

### Set as factors several variables
```{r}
datos <- subset(datos, select = -Time)

datos$Obs <- as.factor(datos$Obs)
datos$PatientID <- as.factor(datos$PatientID)
datos$Activity <- as.factor(datos$Activity)

summary(datos)
datos
```

Those observations with 0 are transformed to NA (it is not possible for a living person to have 0 rpm)
```{r}
datos[datos == 0 & sapply(datos, is.numeric)] <- NA
summary(datos$PatientID)
```


```{r}
table(datos$PatientID, datos$Activity)

```


```{r}
sum(is.na(datos))
tapply(rowSums(is.na(datos)), datos$PatientID, sum)
```

```{r}
colSums(is.na(datos))

datos[!complete.cases(datos), ]
```


```{r}
round(colMeans(is.na(datos)) * 100, 3)

```

```{r}
hist(datos$RRppg1)
hist(datos$RRppg2)

summary(datos$RRppg1)
summary(datos$RRppg2)
```


With this it can be seen the large amount of missing data from the study.
```{r}

library(tidyverse)

devices <- c("RRox","RRcm1","RRcm2","RRppg1","RRppg2","RRimp","RRacc","RRcb")
colores <- c(
  "RRox"   = "#1F78B4",
  "RRcm1"  = "#E31A1C", 
  "RRcm2"  = "#FF7F00", 
  "RRppg1" = "#33A02C", 
  "RRppg2" = "#6A3D9A",
  "RRimp"  = "#B15928",
  "RRacc"  = "#20B2AA",
  "RRcb"   = "#FF69B4")

datos_long <- datos %>%
  pivot_longer(all_of(devices), names_to = "Device", values_to = "RR")

datos_long %>%
  dplyr::filter(Device != "RRox") %>%
  group_by(Device) %>%
  summarise(pct_na = mean(is.na(RR)) * 100) %>%
  dplyr::filter(pct_na > 0) %>%
  mutate(Device = fct_reorder(Device, pct_na)) %>%
  ggplot(aes(x = Device, y = pct_na, fill = Device)) +
  geom_col(alpha = 0.8) +
  geom_text(aes(label = paste0(round(pct_na), "%")), hjust = -0.2, size = 3.5) +
  scale_fill_manual(values = colores) +
  coord_flip(ylim = c(0, 60)) +
  labs(title = "% NA by device", x = NULL, y = "% NAs") +
  theme_minimal() + theme(legend.position = "none")
```

```{r}
library(dplyr)
library(tidyr)

datos %>%
  group_by(Activity) %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(-Activity,
               names_to = "Variable",
               values_to = "Missing") %>%
  dplyr::filter(Missing > 0)
```

```{r}
unique(datos$Activity)

```

```{r}
boxplot(datos[sapply(datos, is.numeric)],
        las = 2,
        col = "lightblue")
```

```{r}
par(mfrow = c(3,3))

for(i in names(datos)){
  if(is.numeric(datos[[i]])){
    hist(datos[[i]], main = i, col = "lightblue")
  }
}
```

```{r}
library(ggplot2)

# Boxplot RRox (gold standard) by activity
ggplot(datos, aes(x = Activity, y = RRox)) +
  geom_boxplot(fill = "steelblue", outlier.colour = "red") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "RRox by activity", y = "RR")
```

```{r}
library(tidyverse)

# devices avaliable
devices <- c("RRox", "RRcm1", "RRcm2", "RRppg1", "RRppg2", "RRimp", "RRacc", "RRcb")

# to detect outliers (1.5*IQR)
detectar_outliers <- function(x) {
  Q1 <- quantile(x, 0.25, na.rm = TRUE)
  Q3 <- quantile(x, 0.75, na.rm = TRUE)
  IQR <- Q3 - Q1
  x < (Q1 - 1.5 * IQR) | x > (Q3 + 1.5 * IQR)
}
```



```{r}
outliers_tabla <- datos %>%
  pivot_longer(cols = all_of(devices), 
               names_to = "Device", 
               values_to = "RR") %>%
  group_by(Device) %>%
  mutate(es_outlier = detectar_outliers(RR)) %>%
  dplyr::filter(es_outlier == TRUE) %>%
  dplyr::select(PatientID, Activity, Device, RR) %>%
  arrange(Device, Activity)

print(outliers_tabla)
```

```{r}
resumen_outliers <- outliers_tabla %>%
  group_by(Activity, Device) %>%
  summarise(n_outliers = n(), .groups = "drop") %>%
  pivot_wider(names_from = Device, values_from = n_outliers, values_fill = 0)

print(resumen_outliers)
```

```{r}
datos_long %>%
  filter(!is.na(RR)) %>%
  ggplot(aes(Device, RR, fill = Device)) +
  geom_boxplot(alpha = 0.7) +
  geom_hline(yintercept = 20, linetype = "dashed", color = "red") +
  scale_fill_manual(values = colores) +
  labs(title = "RR by device", y = "RR (resp/min)") +
  theme_minimal()
```


The following scatter plots are done excluding the NAs, so it is not reliable.
```{r}
datos_long %>%
  filter(Device != "RRox", !is.na(RR)) %>%
  left_join(select(datos, PatientID, Obs, RRox), by = c("PatientID", "Obs")) %>%
  filter(!is.na(RRox)) %>%
  ggplot(aes(x = RRox, y = RR, color = Device)) +
  geom_point(alpha = 0.3, size = 1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ Device, scales = "free", nrow = 2) +
  scale_color_manual(values = colores) +
  labs(title = "Devices vs. RRox (goldstandard)", x = "RRox (resp/min)", y = "Device (resp/min)") +
  theme_minimal()
```

```{r}
datos_long %>%
  filter(!is.na(RR)) %>%
  ggplot(aes(x = RR, fill = Device)) +
  geom_histogram(bins = 20, alpha = 0.8, color = "white") +
  geom_vline(xintercept = 20, linetype = "dashed", color = "red") +
  facet_wrap(~ Device, nrow = 2) +
  scale_fill_manual(values = colores) +
  labs(title = "RR distribution by device", x = "RR (resp/min)", y = "Frequency") +
  theme_minimal() + theme(legend.position = "none")
```



# BAYESIAN vs FREQUENTIST ANALYSIS: RR vs Gold Standard (RRox)
```{r}
cache = TRUE
library(brms)
library(tidyverse)
library(posterior)
library(DescTools)
library(readxl)

# Parameters
DATA_PATH  <- "pone.0168321.s003.xlsx"
DELTA <- 6      # ±6 rpm: clinically accepted range
CP_TARGET <- 0.80   # Coverage Probability
P_TARGET <- 0.70   # Bayesian threshold
MAX_MISS <- 0.20   # exclude if >20% NAs in device × activity
MIN_N <- 15     # min. valid n by analysis

DEVICES <- c(
  RRcm1 = "Camera-1", RRcm2 = "Camera-2",
  RRppg1 = "PPG-1",   RRppg2 = "PPG-2",
  RRimp = "Impedance", RRacc = "Accelerometer", RRcb = "Chest-band"
)
DEVICE_BY_ACTIVITY <- c(
  RRcb = "Chest-band"   # only Chest-band for analysis by activity
)

priors <- c(
  prior(normal(0, 15),      class = "Intercept"),
  prior(student_t(3, 0, 5), class = "sd"),
  prior(student_t(3, 0, 5), class = "sigma")
)
```


## DATA

```{r}
raw <- read_excel(DATA_PATH)
cat("Data:", nrow(raw), "observations |",
    n_distinct(raw$PatientID), "patients |",
    n_distinct(raw$Activity), "activities \n\n")

# Exclude activities with >MAX_MISS NAs for a device
filter_by_missing <- function(df, dev) {
  df %>%
    group_by(Activity) %>%
    mutate(pct_miss = mean(is.na(.data[[dev]]))) %>%
    ungroup() %>%
    filter(pct_miss <= MAX_MISS) %>%
    select(-pct_miss)
}
```

## FREQUENTIST METRICS (PARKER)

```{r}
freq_metrics <- function(df, dev) {
  d <- df %>%
    transmute(gold = RRox, device = .data[[dev]], diff = device - gold) %>%
    drop_na()

  n <- nrow(d)
  bias <- mean(d$diff)
  s <- sd(d$diff)
  se <- s / sqrt(n)

  list(
    n = n,
    bias = bias,
    bias_lo = bias - 1.96 * se,
    bias_hi = bias + 1.96 * se,
    loa_l = bias - 1.96 * s,
    loa_u = bias + 1.96 * s,
    cp = mean(abs(d$diff) <= DELTA),
    tdi = as.numeric(quantile(abs(d$diff), 0.95)),
    ccc = tryCatch(CCC(d$gold, d$device)$rho.c$est, error = function(e) NA_real_),
    cia = tryCatch(1 - (s^2 + bias^2) / (2 * var(d$gold)), error = function(e) NA_real_)
  )
}
```


# BAYESIAN MODEL + METICS

```{r}
# 'by_activity': TRUE = just random effect of patient
#                FALSE = random effects of patient + activity

fit_bayes <- function(df, dev, by_activity = FALSE) {
  d <- df %>%
    transmute(
      id       = factor(PatientID),
      activity = factor(Activity),
      diff     = .data[[dev]] - RRox
    ) %>%
    drop_na()

  formula <- if (by_activity) {
    diff ~ 1 + (1 | id)                    # in an activity: just patient
  } else {
    diff ~ 1 + (1 | id) + (1 | activity)  # global: patient + activity
  }

  fit <- brm(
    formula,
    data    = d,
    family  = gaussian(),
    prior   = priors,
    chains  = 4, iter = 4000, warmup = 1000, seed = 42,
    control = list(adapt_delta = 0.95),
    silent  = 2, refresh = 0
  )

  draws <- as_draws_df(fit)

  sigma_tot <- if (by_activity) {
    sqrt(draws$sd_id__Intercept^2 + draws$sigma^2)
  } else {
    sqrt(draws$sd_id__Intercept^2 + draws$sd_activity__Intercept^2 + draws$sigma^2)
  }

  bias     <- draws$b_Intercept
  cp_draws <- pnorm(DELTA, bias, sigma_tot) - pnorm(-DELTA, bias, sigma_tot)

  out <- list(
    fit = fit,
    bias_mean  = mean(bias),
    bias_lo = as.numeric(quantile(bias, 0.025)),
    bias_hi = as.numeric(quantile(bias, 0.975)),
    loa_l_mean = mean(bias - 1.96 * sigma_tot),
    loa_l_lo = as.numeric(quantile(bias - 1.96 * sigma_tot, 0.025)),
    loa_l_hi = as.numeric(quantile(bias - 1.96 * sigma_tot, 0.975)),
    loa_u_mean = mean(bias + 1.96 * sigma_tot),
    loa_u_lo = as.numeric(quantile(bias + 1.96 * sigma_tot, 0.025)),
    loa_u_hi = as.numeric(quantile(bias + 1.96 * sigma_tot, 0.975)),
    sigma_pat = mean(draws$sd_id__Intercept),
    sigma_res = mean(draws$sigma),
    sigma_tot = mean(sigma_tot),
    cp_mean = mean(cp_draws),
    cp_lo = as.numeric(quantile(cp_draws, 0.025)),
    cp_hi = as.numeric(quantile(cp_draws, 0.975)),
    p_cp_ok = mean(cp_draws >= CP_TARGET),
    tdi_mean = mean(qnorm(0.95, abs(bias), sigma_tot)),
    cp_draws = as.numeric(cp_draws)
  )

  # sigma of activity only in the global model
  if (!by_activity) {
    out$sigma_act <- mean(draws$sd_activity__Intercept)
  }

  out
}
```


# TO PRINT RESULTS

```{r}
print_results <- function(f, b, label = "") {
  cat(sprintf("\n [FREQUENTIST%s]\n", label))
  cat(sprintf("  Bias: %.2f [%.2f, %.2f]  LoA: [%.2f, %.2f]\n",
              f$bias, f$bias_lo, f$bias_hi, f$loa_l, f$loa_u))
  cat(sprintf("  CP: %.1f%%   TDI: %.2f   CCC: %.3f   CIA: %.3f\n",
              100 * f$cp, f$tdi, f$ccc, f$cia))

  cat(sprintf("\n [BAYESIAN%s]\n", label))
  cat(sprintf("  Bias: %.2f [%.2f, %.2f]  LoA: [%.2f, %.2f]\n",
              b$bias_mean, b$bias_lo, b$bias_hi, b$loa_l_mean, b$loa_u_mean))
  cat(sprintf("  LoA CrI: [%.2f-%.2f , %.2f-%.2f]\n",
              b$loa_l_lo, b$loa_l_hi, b$loa_u_lo, b$loa_u_hi))
  cat(sprintf("  CP: %.1f%% [%.1f%%, %.1f%%]   TDI: %.2f rpm\n",
              100 * b$cp_mean, 100 * b$cp_lo, 100 * b$cp_hi, b$tdi_mean))

  if (!is.null(b$sigma_act)) {
    cat(sprintf("  sigma: patient=%.2f  activity=%.2f  residual=%.2f\n",
                b$sigma_pat, b$sigma_act, b$sigma_res))
  } else {
    cat(sprintf("  sigma: patient=%.2f  residual=%.2f\n",
                b$sigma_pat, b$sigma_res))
  }

  cat(sprintf("\n [JUST BAYES] P(CP >= %.0f%%) = %.1f%%  ->  %s\n",
              100 * CP_TARGET, 100 * b$p_cp_ok,
              ifelse(b$p_cp_ok >= P_TARGET, "RECOMMENDED", "NOT RECOMMENDED")))
}
```


# GLOBAL ANALYSIS

```{r}
results_global <- list()

for (dev in names(DEVICES)) {
  dname  <- DEVICES[[dev]]
  df_dev <- filter_by_missing(raw, dev)
  n_kept <- sum(!is.na(df_dev[[dev]]) & !is.na(df_dev$RRox))
  n_excl <- nrow(raw) - nrow(df_dev)

  cat("═══════════════════════════════════════════════════\n")
  cat(sprintf(" GLOBAL | %s\n", dname))
  cat("═══════════════════════════════════════════════════\n")
  cat(sprintf(" Valid pairs: %d  |  Excluded by >20%% NAs: %d\n", n_kept, n_excl))

  if (n_kept < MIN_N) { cat(" Not enough data. Not included\n\n"); next }

  f <- freq_metrics(df_dev, dev)
  b <- fit_bayes(df_dev, dev, by_activity = FALSE)

  act_cp <- df_dev %>%
    transmute(activity = Activity, diff = .data[[dev]] - RRox) %>%
    drop_na() %>%
    group_by(activity) %>%
    summarise(n = n(), cp = mean(abs(diff) <= DELTA), .groups = "drop") %>%
    arrange(desc(cp))

  results_global[[dev]] <- list(dname = dname, freq = f, bayes = b,
                                 activity = act_cp, df_dev = df_dev)

  print_results(f, b)

  cat("\n [CP frequentist by activity]:\n")
  act_cp %>%
    mutate(label = sprintf("  %-14s n=%3d  CP=%.1f%%\n", activity, n, 100*cp)) %>%
    pull(label) %>% cat()

  cat("\n")
}

```



# ANALYSIS BY ACTIVITY (just chest-band)

```{r}
results_act <- list()
activities  <- sort(unique(raw$Activity))

for (dev in names(DEVICE_BY_ACTIVITY)) {
  dname <- DEVICE_BY_ACTIVITY[[dev]]

  cat("═══════════════════════════════════════════════════\n")
  cat(sprintf(" BY ACTIVITY | %s\n", dname))
  cat("═══════════════════════════════════════════════════\n")

  for (act in activities) {
    df_sub <- raw %>%
      filter(Activity == act) %>%
      mutate(pct_miss = mean(is.na(.data[[dev]]) | is.na(RRox))) %>%
      filter(pct_miss <= MAX_MISS) %>%
      select(-pct_miss)

    n_valid   <- sum(!is.na(df_sub[[dev]]) & !is.na(df_sub$RRox))
    pct_miss  <- mean(is.na(raw[[dev]][raw$Activity == act]) |
                      is.na(raw$RRox[raw$Activity == act]))

    cat(sprintf(" %-18s | n=%d | NA=%.1f%%", act, n_valid, 100 * pct_miss))

    if (pct_miss > MAX_MISS) { cat("  -> Excluded (>20% NAs)\n"); next }
    if (n_valid  < MIN_N)    { cat("  -> Not enough data \n"); next }
    cat("  -> Analized\n")

    f <- freq_metrics(df_sub, dev)
    b <- fit_bayes(df_sub, dev, by_activity = TRUE)

    key <- paste(dev, act, sep = "__")
    results_act[[key]] <- list(dname = dname, activity = act,
                                dev = dev,
                                freq = f, bayes = b,
                                df_sub = df_sub)

    print_results(f, b, label = paste0(" | ", act))
    cat("\n")
  }
}
```



# SUMMARY TABLES

```{r}
cat("═══════════════════════════════════════════════════\n")
cat(" GOBAL SUMMARY - DEVICES \n")
cat("═══════════════════════════════════════════════════\n\n")

map_dfr(names(results_global), function(dev) {
  f <- results_global[[dev]]$freq
  b <- results_global[[dev]]$bayes
  tibble(
    Dispositivo = results_global[[dev]]$dname,
    n = f$n,
    Bias = round(b$bias_mean, 2),
    LoA = sprintf("[%.1f, %.1f]", b$loa_l_mean, b$loa_u_mean),
    CP_freq = sprintf("%.1f%%", 100 * f$cp),
    CP_bayes = sprintf("%.1f%% [%.1f%%, %.1f%%]",
                          100*b$cp_mean, 100*b$cp_lo, 100*b$cp_hi),
    `P(CP>=80%)` = sprintf("%.1f%%", 100 * b$p_cp_ok),
    TDI = round(b$tdi_mean, 2),
    CCC = round(f$ccc, 3),
    CIA = round(f$cia, 3),
    Veredicto = ifelse(b$p_cp_ok >= P_TARGET, "RECOMMENDED", "No")
  )
}) %>% print(n = Inf, width = Inf)

cat("\n═══════════════════════════════════════════════════\n")
cat(" SUMMARY BY ACTIVITY - Chest-band\n")
cat("═══════════════════════════════════════════════════\n\n")

map_dfr(names(results_act), function(k) {
  f <- results_act[[k]]$freq
  b <- results_act[[k]]$bayes
  tibble(
    Actividad = results_act[[k]]$activity,
    n = f$n,
    Bias = round(b$bias_mean, 2),
    LoA = sprintf("[%.1f, %.1f]", b$loa_l_mean, b$loa_u_mean),
    CP_freq = sprintf("%.1f%%", 100 * f$cp),
    CP_bayes = sprintf("%.1f%% [%.1f%%, %.1f%%]",
                           100*b$cp_mean, 100*b$cp_lo, 100*b$cp_hi),
    `P(CP>=80%)` = sprintf("%.1f%%", 100 * b$p_cp_ok),
    TDI = round(b$tdi_mean, 2),
    CCC = round(f$ccc, 3),
    CIA = round(f$cia, 3),
    Veredicto = ifelse(b$p_cp_ok >= P_TARGET, "RECOMMENDED", "No")
  )
}) %>%
  arrange(desc(readr::parse_number(`P(CP>=80%)`))) %>%
  print(n = Inf, width = Inf)

```


## GRAPHS

```{r}

# Bland-Altman global by device
for (dev in names(results_global)) {
  r   <- results_global[[dev]]
  b   <- r$bayes
  obs <- r$df_dev %>%
    transmute(avg = (.data[[dev]] + RRox) / 2,
              diff = .data[[dev]] - RRox,
              activity = Activity) %>% drop_na()

  print(
    ggplot(obs, aes(avg, diff, colour = activity)) +
      geom_point(alpha = 0.7, size = 1.8) +
      geom_hline(yintercept = b$bias_mean, linewidth = 0.9) +
      geom_hline(yintercept = c(b$loa_l_mean, b$loa_u_mean),
                 linetype = "dashed", linewidth = 0.8) +
      geom_hline(yintercept = c(-DELTA, DELTA),
                 linetype = "dotted", colour = "red", linewidth = 0.6) +
      labs(title    = paste("Bayesian Bland-Altman (global):", r$dname),
           subtitle = sprintf("Bias=%.2f [%.2f,%.2f]  LoA=[%.2f,%.2f]  CP=%.1f%%",
                              b$bias_mean, b$bias_lo, b$bias_hi,
                              b$loa_l_mean, b$loa_u_mean, 100*b$cp_mean),
           x = "(Device + Gold)/2 (rpm)", y = "Device - Gold (rpm)",
           colour = "Activity") +
      theme_bw(base_size = 11)
  )
}

# Bland-Altman by activity (Chest-band)
for (k in names(results_act)) {
  r   <- results_act[[k]]
  b   <- r$bayes
  obs <- r$df_sub %>%
    transmute(avg  = (.data[[r$dev]] + RRox) / 2,
              diff = .data[[r$dev]] - RRox) %>% drop_na()

  print(
    ggplot(obs, aes(avg, diff)) +
      geom_point(alpha = 0.7, size = 1.8, colour = "#2c7bb6") +
      geom_hline(yintercept = b$bias_mean, linewidth = 0.9) +
      geom_hline(yintercept = c(b$loa_l_mean, b$loa_u_mean),
                 linetype = "dashed", linewidth = 0.8) +
      geom_hline(yintercept = c(-DELTA, DELTA),
                 linetype = "dotted", colour = "red", linewidth = 0.6) +
      labs(title    = paste("Bayesian Bland-Altman:", r$dname, "|", r$activity),
           subtitle = sprintf("Bias=%.2f [%.2f,%.2f]  LoA=[%.2f,%.2f]  CP=%.1f%%",
                              b$bias_mean, b$bias_lo, b$bias_hi,
                              b$loa_l_mean, b$loa_u_mean, 100*b$cp_mean),
           x = "(Device + Gold)/2 (rpm)", y = "Device - Gold (rpm)") +
      theme_bw(base_size = 11)
  )
}

# Heatmap global CP
map_dfr(names(results_global), function(dev) {
  results_global[[dev]]$activity %>%
    mutate(Device = results_global[[dev]]$dname)
}) %>%
  ggplot(aes(Device, activity, fill = cp)) +
  geom_tile(colour = "white") +
  geom_text(aes(label = sprintf("%.0f%%", 100*cp)), size = 3) +
  scale_fill_gradient2(low = "#d73027", mid = "#ffffbf", high = "#1a9850",
                       midpoint = CP_TARGET, limits = c(0,1), name = "CP") +
  labs(title = "Coverage Probability by device and activity",
       subtitle = paste0("Criterion: ±", DELTA, " rpm  |  Activities with >20% NAs excluded"),
       x = NULL, y = NULL) +
  theme_bw(base_size = 11) +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))

# Heatmap P(CP>=80%) by activity (Chest-band)
map_dfr(names(results_act), function(k) {
  b <- results_act[[k]]$bayes
  tibble(Activity  = results_act[[k]]$activity,
         Device = results_act[[k]]$dname,
         p_ok = b$p_cp_ok)
}) %>%
  ggplot(aes(Device, Activity, fill = p_ok)) +
  geom_tile(colour = "white") +
  geom_text(aes(label = sprintf("%.0f%%", 100*p_ok)), size = 3) +
  scale_fill_gradient2(low = "#d73027", mid = "#fee08b", high = "#1a9850",
                       midpoint = P_TARGET, limits = c(0,1), name = "P(recom.)") +
  labs(title = "Bayesian recommendation probability — Chest-band by activity",
       subtitle = sprintf("Recommendable if P(CP >= %.0f%%) >= %.0f%%",
                          100*CP_TARGET, 100*P_TARGET),
       x = NULL, y = NULL) +
  theme_bw(base_size = 11)
```

```{r}
raw %>%
  pivot_longer(cols = c(RRcm2, RRppg2, RRimp, RRacc, RRcb),
               names_to = "Device", values_to = "RR") %>%
  drop_na(RR) %>%
  ggplot(aes(x = RR)) +
  geom_histogram(bins = 20, fill = "#2c7bb6", colour = "white") +
  facet_wrap(~Device, scales = "free") +
  labs(title = "Distribution of RR readings by device",
       x = "Respiratory Rate (rpm)", y = "Count") +
  theme_bw(base_size = 11)
```

```{r}
# Boxplot of each device by activity
raw %>%
  pivot_longer(cols = c(RRcm2, RRppg2, RRimp, RRacc, RRcb),
               names_to = "Device", values_to = "RR") %>%
  ggplot(aes(Activity, RR, fill = Device)) +
  geom_boxplot(outlier.size = 0.8) +
  facet_wrap(~Device, scales = "free") +
  theme_bw(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of RR by device and activity",
       x = NULL, y = "RR (rpm)")

# Heatmap of NAs by device × activity
raw %>%
  pivot_longer(cols = c(RRcm2, RRppg2, RRimp, RRacc, RRcb),
               names_to = "Device", values_to = "val") %>%
  group_by(Device, Activity) %>%
  summarise(pct_na = mean(is.na(val)) * 100, .groups = "drop") %>%
  ggplot(aes(Device, Activity, fill = pct_na)) +
  geom_tile(colour = "white") +
  geom_text(aes(label = sprintf("%.0f%%", pct_na)), size = 3) +
  scale_fill_gradient(low = "white", high = "#d73027", name = "% NA") +
  labs(title = "Missing data (%) by device and activity",
       x = NULL, y = NULL) +
  theme_bw(base_size = 11)

# Table of the valid n by device
raw %>%
  summarise(across(c(RRcm2, RRppg2, RRimp, RRacc, RRcb),
                   list(n = ~sum(!is.na(.)),
                        pct_na = ~round(mean(is.na(.))*100, 1)))) %>%
  pivot_longer(everything()) %>%
  print()
```

